salad

### 2023-01-05 inst/salad.Rmd
use samep.test()

From row 3, for exampl,e we see that salad `A` was ranked as second
most tart, `B` the most tart, `C` the third most tart, and `D` the
least tart of the four.  We may process this using two methods,
explicit and slick.  First, explicit:

@@

>>>>

From row 3, for example, we see that salad `A` was ranked as second
most tart, `B` the most tart, `C` the third most tart, and `D` the
least tart of the four.  We may process this using two methods,
explicit and slick.  First, explicit:

@@

We may use `hyper2` to test some hypotheses.  Firstly, $H_0\colon
p_B=\frac{1}{4}$, which we test with `specificp.test()`:

```{r specificptestB,cache=TRUE}
specificp.test(H2,"B",1/4)
```

Above we see a $p$-value of about $10^{-7}$, clearly significant.
However, we may also test the hypothesis that $p_B$ is less than the
second strongest, $p_C$:

```{r sameptestBC,cache=TRUE}
samep.test(H2,c("B","C"))
```

We see a $p$-value of about $7\times 10^{-4}$, much higher than the
value from `specificp.test()` of $H_0\colon p_B=\frac{1}{4}$.  This is
because `samep.test()` allows one to change the value of $p_C$ and we
would expect a less significant result.
